---
title: "Scraping Wikpedia Tables"
author: "Adam J Campbell"
date: 2020-06-23
output: html_document
draft: True
summary: A quick how-to guide on scraping tables from wikipedia, using R.
---

I was recently attempting to scrape a table from [Wikipedia](https://en.wikipedia.org/wiki/Main_Page).  I wanted something very quick since I was responding to a group chat and wanted to make a quick histogram (something I love about R and ggplot).  I came across this tweet from [Julia Silge](https://twitter.com/juliasilge):

```{r echo=FALSE}
blogdown::shortcode('tweet', '951639629182074880')
```

However there are two problems with this

1. the tag for table has changed. and it may change in the future since Wikipedia a living document.
2. if you want to use this on other tables in Wikipedia, it's not entirely obvious, what you need to change.

Problem 1 was address by [David Bishop](https://twitter.com/TheBishop) in this tweet:
```{r echo=FALSE}
blogdown::shortcode('tweet', '1024040452230664192')
```

For problem 2, I'll show you how to change the above code into a code to scrape the table I was interested in, which was the [attendance size of Trump's rallies](https://en.wikipedia.org/wiki/List_of_rallies_for_the_2016_Donald_Trump_presidential_campaign).  Here, I'd like to scrape the `Primary rallies (June 2015–June 2016) ` table.

The first thing to change is the `read_html()` line:

`read_html("https://en.wikipedia.org/wiki/Current_members_of_the_United_States_House_of_Representatives")`

all we need to here is update the hyperlink:

`read_html("https://en.wikipedia.org/wiki/List_of_rallies_for_the_2016_Donald_Trump_presidential_campaign")`

The next thing you'll have to change is the `html_node()` line.  To this this you'll have to know the tag of the table in the html code.  To find this you'll have to [inspect the html code](https://www.lifewire.com/get-inspect-element-tool-for-browser-756549) of the wikipedia page you're looking at.

Inspect the table you're interested in and you'll see a line starting `<table class= ...`
Right click on that line and select `Copy` -> `CSS Selector`

In my case this returns:
`table.wikitable:nth-child(17)`

You can then update the `html_node` line by c 

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(rvest)
h <- read_html("https://en.wikipedia.org/wiki/List_of_rallies_for_the_2016_Donald_Trump_presidential_campaign")

rallies <- h %>%
    html_node("#mw-content-text > div > table:nth-child(17)") %>%
    #html_node("table#votingmembers") %>%
    html_table()

```
